Networked Character Devices

### 2011-12-10 report/presentation.tex
presentation: kill trailing whitespace
presentation: introduction and related work
Added goals page

\title[NCD]{Networked Character Devices}
%\subtitle[]{}
\author[Monaco, Sayler, Spear]{Matthew Monaco \&
                               Andrew Sayler \&
                               Landon Spear}
\institute[CU-Boulder]{
  University of Colorado at Boulder \\
  \texttt{\{first.last\}@colorado.edu}
}
\date[Dec. 10, 2011]{Saturday, December 10\textsuperscript{th}, 2011}

@@

\section{Overview}
%---Intro Slide---%
\begin{frame}{\bf NCD Overview}
  We did some stuff, we used some references \cite{ldd3}.
\end{frame}

@@

\section{Related Work}

>>>>

\title[NCD]{Networked Character Devices}
%\subtitle[]{}
\author[Monaco, Sayler, Spear]{Matthew Monaco \&
                               Andrew Sayler \&
                               Landon Spear}
\institute[CU-Boulder]{
  University of Colorado at Boulder \\
  \texttt{matthew.monaco@colorado.edu} \\
  \texttt{andrew.sayler@colorado.edu} \\
  \texttt{landon.spear@colorado.edu}
}
\date[Dec. 10, 2011]{Saturday, December 10\textsuperscript{th}, 2011}

@@

\section{Overview}
%---Intro Slide---%

@@

\begin{frame}{\bf NCD Goals}
  \begin{itemize}
    \item<1-> Export any character device (or file) from a server over IP
    \begin{itemize}
      \item<2-> Client has exclusive access
      \item<3-> User-level advertisment, kernel-level functionality
    \end{itemize}
    \item<4-> Non-locality should be transparent to client's user level operations    
    \begin{itemize}
      \item<5-> Imported devices are accessed as local devices
      \item<6-> All client device accesses are intercepted by kernel module and sent over network
      \item<7-> Server has no access so write conflicts are not a problem
    \end{itemize}
  \end{itemize}
\end{frame}

\begin{frame}{\bf NCD Overview}
  \begin{itemize}
    \item<1-> Stuff
    \item<2-> Motivation: transparent remote device usage
    \item<3-> Client: kernel module (Linux 2.6.x+)
    \item<4-> Server: userspace daemon
    \item<5-> Current Project Status:
    \begin{itemize}
      \item<6-> successful implementation
      \item<6-> rough around the edges
      \item<6-> very clear focus for future work
    \end{itemize}
  \end{itemize}
\end{frame}

\begin{frame}{Related Work}
  \begin{itemize}
    \item nfs
    \item nbd
    \item CUSE
    \item USB/IP Project
  \end{itemize}
\end{frame}
